Analysis of competitive surfing tournaments with generalized Bradley-Terry

### 2021-08-22 inst/surfing_jsa.tex
further dealing with issue #107

The statistical method described here can test many different
suggestions drawn from surfing lore.  For example, one frequent
suggestion {\bf Tim I need citations here} is that Brazilian surfers
such as Ferreira and Toledo have surfing skillsets that favour point
and beach break beaches {\bf Tim I need some help describing and
  defining these here}, those types of beach being readily accessible
to these surfers' native Brazil.  We now assess the null that
Brazilians perform equally well on all types of beaches.  To that end,
we create a reified surfer, ``Brazilian beachtype", whose strength
helps all Brazilian surfers when surfing on their (putative) preferred
beachtype, analogously to the ``home ground monster" who helps the
home team as per equation~\ref{home_ground_advantage}.  The null would
be that this reified entity has zero strength.  We fail to reject this
null (differential support = 0.035; $p=0.79$) and conclude that there
is no evidence to suggest that Brazilians' performce is better on
their preferred beach types than one would expect by chance.  We may
go further using the method of support and state that not only is the
maximum likelihood estimate for Brazilian beachtype is very small
(about 0.002), but we may rule out the suggestion that the strength of
this entity exceeds about 0.025
(Figure~\ref{brazilian_beachtype_support}).

>>>>

The statistical method described here can test many different
suggestions drawn from surfing lore.  For example, one frequent
suggestion {\bf Tim I need citations here} is that Brazilian surfers
such as Ferreira and Toledo have surfing skillsets that favour point
and beach break beaches {\bf Tim I need some help describing and
  defining these here}, those types of beach being readily accessible
to these surfers' native Brazil.  We now assess the null that
Brazilians perform equally well on all types of beaches.  To that end,
we create a reified surfer, ``Brazilian beachtype", whose strength
helps all Brazilian surfers when surfing on their (putative) preferred
beachtype, analogously to the ``home ground monster" who helps the
home team as per equation~\ref{home_ground_advantage}.  Here we modify
the likelihood function only when a single Brazilian is in the water,
to avoid possible interaction with the compatriot issue discussed in
section~\ref{compatriot}.  The null would be that this reified entity
has zero strength.  We fail to reject this null (differential support
= 0.035; $p=0.79$) and conclude that there is no evidence to suggest
that Brazilians' performce is better on their preferred beach types
than one would expect by chance.  We may go further using the method
of support: not only is the maximum likelihood estimate for Brazilian
beachtype very small (about 0.002), but in addition we may reject the
the proposal that the strength of this entity exceeds about 0.025
(Figure~\ref{brazilian_beachtype_support}).
